---
title: "Assignment 4 Q3"
author: "Barbara Rose Hoover"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###3. Describe Lobster Abundance and Fishing Pressure (2012-2017)
####At Isla Vista and Naples Reef, the two protected MPA sites (with zero fishing pressure), how do lobster sizes in 2012 and 2017 compare? At the non-MPA sites?  

```{r include=FALSE}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
library(tadaatoolbox)
```
####Read in Data
```{r Read in data, echo=FALSE}
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")
```



###Data.frame: All 5 sites in Frequency Format  
  - SITE  
      - "AQUE" "CARP" "IVEE" "MOHK" "NAPL"
  - YEAR  
      - 2012, 2017  
  - MPA  
      - Designated (Yes, No) 

Table to include only head of table (out of 1074 observations)
```{r echo=FALSE}
lb_size_3 <- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL", YEAR == "2017" | YEAR == "2012",  COUNT != "0") %>%
  select(YEAR,SITE,SIZE,COUNT) %>% 
  group_by(SITE, YEAR) %>%
  mutate(MPA = ifelse(grepl("IVEE", SITE), "Yes",
                                      ifelse(grepl("NAPL", SITE), "Yes", "No")))
head1<-head(lb_size_3)
head1%>%
  kable() %>%
  kable_styling()
```

###Data.frame: All 5 sites expanded from Frequency to Case Format (n=1,899)
```{r expanded for frequency, echo=FALSE}
sz_expand_3 <- lb_size_3[rep(1:nrow(lb_size_3), lb_size_3[["COUNT"]]), ]
##sz_expand_3$SITE<-as.factor(sz_expand_3$SITE)
head2<-head(sz_expand_3)
head2%>%
  kable() %>%
  kable_styling()
```
***
###Box Plot 
```{r size box plot inclusive, echo=FALSE}
sz_expand_3$YEAR <- factor(sz_expand_3$YEAR, 
                  levels = c(2012, 2017))

b<-ggboxplot(sz_expand_3, x = "SITE", y = "SIZE", color = "YEAR",
          palette = c("#00AFBB", "#E7B800"))
b
```

***  

###Summary Table  
  - All Sites  
  - Years 2012, 2017
```{r summary table of the years 2012 2017, echo=FALSE}
##detach(package:plyr)
##lb_size_3$YEAR <-as.factor(lb_size_3$YEAR)
size_sum_3 <- sz_expand_3 %>% 
  group_by(YEAR, SITE) %>% 
  summarize('mean' = round(mean(`SIZE`), digits=2),
            'median' = round(median(`SIZE`), digits = 2),
            'max' = max(`SIZE`),
            'SD' = round(sd(`SIZE`),digits=2), 
            'n' = sum(`COUNT`),
            'se' = round(sd(`SIZE`)/sqrt(length(`SIZE`)), digits = 2)) %>% 
  arrange(SITE)

size_sum_3%>%
  kable() %>%
  kable_styling()
```
***
##IVEE (MPA)  


####Visual Data  

```{r IVEE qq plot for visual inspection, echo=FALSE}
ivee_2012_3 <- sz_expand_3 %>% 
  filter(SITE == "IVEE", YEAR == 2012) %>% 
  ungroup() %>% 
  select(SIZE)

ivee_2017_3 <- sz_expand_3 %>% 
  filter(SITE == "IVEE", YEAR == 2017) %>% 
  ungroup() %>% 
  select(SIZE)
```

<div class = "row">
<div class = "col-md-6">
2012
```{r echo=FALSE}
ggqqplot(ivee_2012_3$SIZE)
```
</div>
<div class = "col-md-6">
2017
```{r echo=FALSE}
ggqqplot(ivee_2017_3$SIZE)
```
</div>
</div>

####F test for variance  

```{r IVEE variance test, echo=FALSE}
ivee_var_3<-var.test(ivee_2012_3$SIZE, ivee_2017_3$SIZE)
ivee_var_3
```
RESULT:  
p-value for the variance test, (`r ivee_var_3$p.value`) is larger than the significance level $\alpha$ = 0.05. There is not a significant difference between the variances of the two sets of data. We will need to use student's t-test, which is designed for equal variances, and the assumption of normality.  

####Shapiro-Wilk normality test  
2012 sample size is <30 (n=28) 
```{r IVEE shapiro test for normality, echo=FALSE}
ivee_sw_3<-shapiro.test(ivee_2012_3$SIZE)
ivee_sw_3
```
p-value = 0.0003044

RESULT:  
From the output, the p-value (`r ivee_sw_3$p.value`) < 0.05 implying that the distribution of the data are significantly different from normal distribution. In other words, we cannot assume the normality, and will have to use Welch's t-test. 

#### T-test
```{r ivee t test, echo=FALSE }
ivee_t_3 <- t.test(ivee_2012_3$SIZE, ivee_2017_3$SIZE) 
ivee_t_3
```
RESULT:  
Mean Lobster Sizes differ significantly between the 2012 and 2017 at IVEE at the 0.05 confidence level. (t(`r round(ivee_t_3$parameter, 2)`) = `r round(ivee_t_3$statistic, 2)`, *p* = `r ivee_t_3$p.value`).


***
##NAPL (MPA)
#####Visual data

```{r NAPL visual data inspection, echo=FALSE}
napl_2012_3 <- sz_expand_3 %>% 
  filter(SITE == "NAPL", YEAR == 2012) %>% 
  ungroup() %>% 
  select(SIZE)

napl_2017_3 <- sz_expand_3 %>% 
  filter(SITE == "NAPL", YEAR == 2017) %>% 
  ungroup() %>% 
  select(SIZE)
```

<div class = "row">
<div class = "col-md-6">
2012
```{r, echo=FALSE}
ggqqplot(napl_2012_3$SIZE)
```
</div>

<div class = "col-md-6">
2017
```{r, echo=FALSE}
ggqqplot(napl_2017_3$SIZE)
```
</div>
</div>  

####Shapiro-Wilk’s test for normality (n<30) 
NAPL 2012 sample size is <30 (n=8)
```{r shapiro test for normality, echo=FALSE}
napl_sw_3<-shapiro.test(napl_2012_3$SIZE)
napl_sw_3
```
p-value = 0.5209

RESULT:  
From the output, the p-value (`r napl_sw_3$p.value`) > 0.05 implying that the distribution of the data are not significantly different from normal distribution. In other words, we can assume the normality.

####F test for variance

```{r napl variance test, echo=FALSE}
napl_var_3<- var.test(napl_2012_3$SIZE, napl_2017_3$SIZE)
napl_var_3
```

RESULT:  
p-value for the variance test, (`r napl_var_3$p.value`) is larger than the significance level $\alpha$ = 0.05. There is not a significant difference between the variances of the two sets of data. We will need to use student's t-test, which is designed for equal variances, and the assumption of normality.

####T-test 

```{r napl t test, echo=FALSE}
napl_t_3 <- t.test(napl_2012_3$SIZE, napl_2017_3$SIZE, var.equal = TRUE) 
napl_t_3
```
RESULT:  
Mean Lobster Sizes do not differ significantly between the 2012 and 2017 at NAPL at the 0.05 confidence level. (t(`r round(napl_t_3$parameter, 2)`) = `r round(napl_t_3$statistic, 2)`, *p* = `r napl_t_3$p.value`).  

***  

##AQUE  


```{r AQUE, echo=FALSE}
aque_2012_3 <- sz_expand_3 %>%
  filter(SITE == "AQUE", YEAR == 2012) %>%
  ungroup() %>%
  select(SIZE)
aque_2017_3 <- sz_expand_3 %>% 
  filter(SITE == "AQUE", YEAR == 2017) %>% 
  ungroup() %>% 
  select(SIZE)
```

<div class = "row">
<div class = "col-md-6">
2012
```{r, echo=FALSE}
ggqqplot(aque_2012_3$SIZE)
```
</div>
<div class = "col-md-6">
2017
```{r, echo=FALSE}
ggqqplot(aque_2017_3$SIZE)
```
</div>
</div>

####F test for variance

```{r aque variance test, echo=FALSE}
aque_var_3<- var.test(aque_2012_3$SIZE, aque_2017_3$SIZE)
aque_var_3
```

RESULT:  
p-value for the variance test, (`r aque_var_3$p.value`) is larger than the significance level $\alpha$ = 0.05. There is not a significant difference between the variances of the two sets of data. We will need to use student's t-test, which is designed for equal variances, and the assumption of normality.

####T-test
```{r aque t test, echo=FALSE}
aque_t_3 <- t.test(aque_2012_3$SIZE, aque_2017_3$SIZE, var.equal = TRUE) 
aque_t_3
```

RESULT:  
Mean Lobster Sizes do not differ significantly between the 2012 and 2017 at AQUE at significance level $\alpha$ = 0.05. (t(`r round(aque_t_3$parameter, 2)`) = `r round(aque_t_3$statistic, 2)`, *p* = `r aque_t_3$p.value`). 

***
##MOHK
####Visual Data
```{r MOHK, echo=FALSE}
mohk_2012_3 <- sz_expand_3 %>% 
  filter(SITE == "MOHK", YEAR == 2012) %>% 
  ungroup() %>% 
  select(SIZE)

mohk_2017_3 <- sz_expand_3 %>% 
  filter(SITE == "MOHK", YEAR == 2017) %>% 
  ungroup() %>% 
  select(SIZE)
```

<div class = "row">
<div class = "col-md-6">
2012
```{r, echo=FALSE}
ggqqplot(mohk_2012_3$SIZE)
```
</div>
<div class = "col-md-6">
2017
```{r echo=FALSE}
ggqqplot(mohk_2017_3$SIZE)
```
</div>
</div>

####F-test for variance 

```{r mohk variance test, echo=FALSE}
mohk_var_3<- var.test(mohk_2012_3$SIZE, mohk_2017_3$SIZE)
mohk_var_3
```
RESULT:  
p-value for the variance test, (`r mohk_var_3$p.value`) is larger than the significance level $\alpha$ = 0.05. There is not a significant difference between the variances of the two sets of data. We will need to use student's t-test, which is designed for equal variances, and the assumption of normality.

###T-test

```{r mohk t test, echo=FALSE}
mohk_t_3 <- t.test(mohk_2012_3$SIZE, mohk_2017_3$SIZE, var.equal = TRUE) 
mohk_t_3
```
RESULT:  
Mean Lobster Sizes differ significantly between the 2012 and 2017 at MOHK at significance level $\alpha$ = 0.05. (t(`r round(mohk_t_3$parameter, 2)`) = `r round(mohk_t_3$statistic, 2)`, *p* = `r mohk_t_3$p.value`). 

***
##CARP
####Visual Data
```{r CARP, echo=FALSE}
carp_2012_3 <- sz_expand_3 %>% 
  filter(SITE == "CARP", YEAR == 2012) %>% 
  ungroup() %>% 
  select(SIZE)

carp_2017_3 <- sz_expand_3 %>% 
  filter(SITE == "CARP", YEAR == 2017) %>% 
  ungroup() %>% 
  select(SIZE)

```

<div class = "row">
<div class = "col-md-6">
2012
```{r, echo=FALSE}
ggqqplot(carp_2012_3$SIZE)
```
</div>
<div class = "col-md-6">
2017
```{r, echo=FALSE}
ggqqplot(carp_2017_3$SIZE)
```
</div>
</div>
####F-test for variance 

```{r CARP variance test, echo=FALSE}
carp_var_3<- var.test(carp_2012_3$SIZE, carp_2017_3$SIZE)
carp_var_3
```
RESULT:   
p-value for the variance test, (`r carp_var_3$p.value`) is larger than the significance level $\alpha$ = 0.05. There is not a significant difference between the variances of the two sets of data. We will need to use student's t-test, which is designed for equal variances, and the assumption of normality.

####T-test 

```{r carp t test, echo=FALSE}
carp_t_3 <- t.test(carp_2012_3$SIZE, carp_2017_3$SIZE, var.equal = T) 
carp_t_3
```

RESULT:  
Mean Lobster Sizes do not differ significantly between the 2012 and 2017 at CARP at the 0.05 confidence level. (t(`r round(carp_t_3$parameter, 2)`) = `r round(carp_t_3$statistic, 2)`, *p* = `r carp_t_3$p.value`). 


