---
title: "Assignment 4 Q2"
author: "Barbara Rose Hoover"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
```


#2.Compare Mean Lobster Size in 2017

```{r}
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")

lb_size_2 <- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL", YEAR == "2017",  COUNT != "0") %>%
  select(YEAR,SITE,SIZE,COUNT) 



sz_expand_2 <- lb_size_2[rep(1:nrow(lb_size_2), lb_size_2[["COUNT"]]), ]
sz_expand_2$SITE<-as.factor(sz_expand_2$SITE)
sz_expand_2

```


###Null hypothesis: the means of the different groups are the same
###Alternative hypothesis: At least one sample mean is not equal to the others.
```{r}
lb_sz_2 <- sz_expand_2 %>% 
  group_by(SITE) %>%
  summarize(count = n(), mean = mean(SIZE), sd = sd(SIZE))
lb_sz_2
```

```{r}
library(Rmisc) 
lb_sz_sum_2 <- summarySE(data=sz_expand_2, 
          "SIZE", 
          groupvars="SITE", 
          conf.interval = 0.95)
lb_sz_sum_2 
```
####Box Plot of Lobster Size Distribution 
```{r data visualization}
sz_bplot_2<-ggboxplot(sz_expand_2, x = "SITE", y = "SIZE", 
          color = "SITE", palette = get_palette(c("#00AFBB", "#E7B800", "#FC4E07"), 5),
          order = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"),
          ylab = "SIZE", xlab = "SITE")
sz_bplot_2
```
####Histogram Representation of Lobster Size Distribution with Means (Totally Unnecessary- It's just pretty)
```{r}
sz_hst_2<-gghistogram(sz_expand_2, x = "SIZE",
   add = "mean", rug = TRUE,
   color = "SITE", fill = "SITE",
   palette = get_palette(c("#00AFBB", "#E7B800", "#FC4E07"), 5),
   xlab = 'Lobster Size')
sz_hst_2
```


##One Way Anova
###As the p-value is less than the significance level 0.05, we can conclude that there are significant differences between the groups highlighted with “*" in the model summary.
```{r one way anova}
lb.aov <- aov(SIZE ~ SITE, data = sz_expand_2)
z<-anova(lb.aov)
summary(lb.aov)
summary(z)
```
####As the ANOVA test is significant, we can compute Tukey HSD (Tukey Honest Significant Differences, R function: TukeyHSD()) for performing multiple pairwise-comparison between the means of groups.

#####NOTE:  
#####The function TukeyHD() takes the fitted ANOVA as an argument.
```{r}
TukeyHSD(lb.aov)
```
####It can be seen from the output, that only the difference between NAPL-IVEE and NAPL-CARP is significant with an adjusted p-value of 0.0037001 & 0.0228728 respectively.  

NAPL-IVEE  4.7799976  1.09751057 8.462485 0.0037001  

NAPL-CARP  4.0023556  0.36042398 7.644287 0.0228728  

####Very close to the significance level. Need to think about this in discussion.  

NAPL-MOHK  4.2321429 -0.08607271 8.550358 0.0579286

```{r}
library(agricolae)

(HSD.test(lb.aov, "SITE"))     
```

lb_sz_sum_2

```{r}
offset.v = -5     # offsets for mean letters
offset.h = 0.6

ggplot(lb_sz_sum_2, 
       aes(x = SITE, y = SIZE, 
           ymax=90, ymin=0.0))  +
       geom_bar(stat="identity", fill="gray50",
           colour = "black", width = 0.7)  +
       geom_errorbar(aes(ymax=SIZE+sd, ymin=SIZE-sd), 
                     width=0.3, size=0.5, color="black")  +
       geom_text(aes(label=c("ab","b","b","b","a"),
                 hjust=offset.h, vjust=offset.v)) +              
       labs(x = "Sample location", 
            y = "Mean Size (mm)")  +
       ggtitle("Mean Lobster Size (mm) by Location") + 
       theme_bw()  +
       theme(panel.grid.major.x = element_blank(),
             panel.grid.major.y = element_line(colour = "grey80"),
             plot.title = element_text(size = rel(1.5), 
             face = "bold", vjust = 1.5),
             axis.title = element_text(face = "bold"),
             axis.title.y = element_text(vjust= 1.8),
             axis.title.x = element_text(vjust= -0.5),
             panel.border = element_rect(colour="black")
             )
```

