---
title: "Assignment 4 Q5"
author: "Barbara Rose Hoover"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
4. Proportions of “legal” lobsters at the 5 sites in 2017
-The legal minimum carapace size for lobster is 82.6 mm. What proportion of observed lobsters at each site
are above the legal minimum? 
-Does that proportion differ significantly across the 5 sites? Note: We’ll be
doing chi-square in labs next week, or go ahead with maximum resourcefulness and check out the chisq.test()
function on your own!

Chi-squared test
Are the observed proportions equal across the 5 sites

```{r load library}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
```

```{r}
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")
```

```{r}
lb_size_5 <- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL", YEAR == "2017", COUNT != "0") %>%
  select(SITE,SIZE,COUNT) %>% 
  group_by(SITE) %>%
  mutate(Count.Legal = ifelse(SIZE > 82.6, "1", "0"))%>%
  mutate(Count.Not.Legal = ifelse(SIZE < 82.6, "1", "0"))
                                      

sz_expand_5 <- lb_size_5[rep(1:nrow(lb_size_5), lb_size_5[["COUNT"]]), ]
sz_expand_5$SITE<-as.character(sz_expand_5$SITE)
sz_expand_5$Count.Legal<-as.integer(sz_expand_5$Count.Legal)
sz_expand_5$Count.Not.Legal<-as.integer(sz_expand_5$Count.Not.Legal)


sz_expand_5
```
```{r}
sz_ratio_5<- sz_expand_5 %>%
    group_by(SITE) %>% 
    summarize ("Legal" = sum(Count.Legal), "Not Legal" = sum(Count.Not.Legal)) %>% 
    mutate('Total' = rowSums(.[2:3])) %>% 
    mutate(MPA = ifelse(grepl("IVEE", SITE), "Yes",
                                      ifelse(grepl("NAPL", SITE), "Yes", "No")))

sz_ratio_5$'Total'<-as.integer(sz_ratio_5$'Total')

sz_percent_5 <- mutate(sz_ratio_5, Percent.Legal = (Legal/Total)*100)

sz_percent_5
```

```{r}
sz_chi_5<-sz_percent_5%>% 
  select(SITE, Legal, `Not Legal`)


row.names(sz_chi_5) <- sz_chi_5$SITE
sz_chi_5[1] <- NULL


sz_chi_5 <- chisq.test(sz_chi_5)
sz_chi_5
sz_chi_5$observed
round(sz_chi_5$expected,2)
round(sz_chi_5$residuals, 3)
```
