---
title: "Assignment 4 Q2"
author: "Barbara Rose Hoover"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
```


#2.Compare Mean Lobster Size in 2017

```{r}
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")

lb_size_2 <- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL", YEAR == "2017",  COUNT != "0") %>%
  select(YEAR,SITE,SIZE,COUNT) 



sz_expand_2 <- lb_size_2[rep(1:nrow(lb_size_2), lb_size_2[["COUNT"]]), ]
sz_expand_2$SITE<-as.factor(sz_expand_2$SITE)
sz_expand_2

```


###Null hypothesis: the means of the different groups are the same
###Alternative hypothesis: At least one sample mean is not equal to the others.
```{r}
lb_sz_2 <- sz_expand_2 %>% 
  group_by(SITE) %>%
  summarize(count = n(), mean = mean(SIZE), sd = sd(SIZE))
lb_sz_2
```

```{r data visualization}
sz_bplot_2<-ggboxplot(sz_expand_2, x = "SITE", y = "SIZE", 
          color = "SITE", palette = get_palette(c("#00AFBB", "#E7B800", "#FC4E07"), 5),
          order = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"),
          ylab = "SIZE", xlab = "SITE")
sz_bplot_2
```

```{r}
sz_hst_2<-gghistogram(sz_expand_2, x = "SIZE",
   add = "mean", rug = TRUE,
   color = "SITE", fill = "SITE",
   palette = get_palette(c("#00AFBB", "#E7B800", "#FC4E07"), 5),
   xlab = 'Lobster Size')
sz_hst_2
```


```{r}
sz_line_2 <- ggline(sz_expand_2, x = "SITE", y = "SIZE",
       add = c("mean_se", "jitter"), 
       order = c("AQUE", "CARP", "IVEE", "MOHK", "NAPL"),
       ylab = "SIZE", xlab = "SITE")
sz_line_2
```

##One Way Anova
###As the p-value is less than the significance level 0.05, we can conclude that there are significant differences between the groups highlighted with “*" in the model summary.
```{r one way anova}
lb.aov <- aov(SIZE ~ SITE, data = sz_expand_2)
summary(lb.aov)
```
###As the ANOVA test is significant, we can compute Tukey HSD (Tukey Honest Significant Differences, R function: TukeyHSD()) for performing multiple pairwise-comparison between the means of groups.

####The function TukeyHD() takes the fitted ANOVA as an argument.
```{r}
TukeyHSD(lb.aov)
```
###It can be seen from the output, that only the difference between NAPL-IVEE and NAPL-CARP is significant with an adjusted p-value of 0.0037001 & 0.0228728 respectively.  

NAPL-IVEE  4.7799976  1.09751057 8.462485 0.0037001  

NAPL-CARP  4.0023556  0.36042398 7.644287 0.0228728 

