---
title: "Assignment 4 Q1"
author: "Barbara Rose Hoover"
date: "11/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
```


###1.	Lobster abundance and fishing pressure (2012 - 2017)
Describe trends in *lobster abundance (counts)* and *fishing pressure (trap buoys)* at the five locations from 2012 - 2017. Ignore transect information - we are only interested in evaluating abundance and pressure on the order of SITE. Note: you are not expected to use regression here - just think of ways to clearly describe annual totals visually and in text, noting important trends, events and differences.

```{r reading in data}
lobster_traps <- read_csv("lobster_traps.csv")
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")
```

#1.Describe Lobster Abundance and Fishing Pressure (2012-2017)
##Lobster Abundance
```{r dataset lobster count by year and site}
##library(plyr)
lb_count_month_year<- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL") %>%
  group_by(SITE, YEAR) %>%
  select(YEAR,SITE,COUNT) 

lb_count_month_year<- aggregate(COUNT~SITE+YEAR, data=lb_count_month_year, sum)
lb_count_month_year<- mutate(lb_count_month_year, MPA = ifelse(grepl("IVEE", SITE), "Yes",
                                      ifelse(grepl("NAPL", SITE), "Yes", "No"))) 
 

lb_count_month_year

```

```{r abundance}
lb_trends_plot<-ggplot(lb_count_month_year, aes(factor(YEAR), COUNT, group = SITE, 
                   color = SITE)) + 
   geom_line(size = 1, alpha = 0.8, aes(linetype = MPA)) +
   geom_point() +
   scale_color_brewer(name = "Location", palette = "Set1")+
   xlab("Year") + 
   ylab("Lobster Count")+
  labs(title = "Lobster Abundance")
lb_trends_plot
```

##Fishing Pressure
```{r dataset fishing pressure}
fishing_pressure_month_year<- lobster_traps %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL") %>%
  group_by(SITE, YEAR, MONTH) %>%
    select(YEAR,SITE,TRAPS)
fishing_pressure_month_year

fishing_pressure_month_year<- aggregate(TRAPS~SITE+YEAR, data=fishing_pressure_month_year, sum)
fishing_pressure_year<- mutate(fishing_pressure_month_year, MPA = ifelse(grepl("IVEE", SITE), "Yes",
                                      ifelse(grepl("NAPL", SITE), "Yes", "No"))) 
 

fishing_pressure_year

```


```{r fishing pressure graph}
fishing_pressure_plot<-ggplot(fishing_pressure_year, aes(factor(YEAR), TRAPS, group = SITE, color = SITE)) + 
   geom_line(size = 1, alpha = 0.8, aes(linetype = MPA)) +
   geom_point() +
   scale_color_brewer(name = "Location", palette = "Set1")+
   xlab("Year") + 
   ylab("Trap Count")+
  labs(title = "Lobster Fishing Pressure")
fishing_pressure_plot
```
