---
title: "Assignment 4 Q3"
author: "Barbara Rose Hoover"
date: "11/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(tidyverse)
library(kableExtra) 
library(knitr)
library(ggplot2)
library(magrittr)
library(ggpubr)
library(cowplot)
library(dplyr)
library(effsize) 
library(vcdExtra)
```


###3. Changes in lobster size at MPA and non-MPA sites (comparing only 2012 and 2017 sizes)

```{r}
setwd("~/Desktop/BREN/ESM 206/Fall 2018/Assignments/Assignment 4")
library(readr)
lobster_size_abundance <- read_csv("lobster_size_abundance.csv")
```

#3.Describe Lobster Abundance and Fishing Pressure (2012-2017)
##At Isla Vista and Naples Reef, the two protected MPA sites (with zero fishing pressure), how do lobster sizes in 2012 and 2017 compare? At the non-MPA sites?

##Dataset to include lobster count by year and site for selected years
###SITE "AQUE" "CARP" "IVEE" "MOHK" "NAPL"
###YEAR (2012 & 2017)
###MPA Designated (Yes, No)
```{r}
library(plyr)
lb_size_3 <- lobster_size_abundance %>%
  filter(SITE == "AQUE" | SITE == "CARP" | SITE == "IVEE" | SITE == "MOHK" | SITE == "NAPL", YEAR == "2017" | YEAR == "2012",  COUNT != "0") %>%
  select(YEAR,SITE,SIZE,COUNT) %>% 
  group_by(SITE, YEAR) %>%
  mutate(MPA = ifelse(grepl("IVEE", SITE), "Yes",
                                      ifelse(grepl("NAPL", SITE), "Yes", "No")))
lb_size_3
```

```{r}
size_sum_3<-lb_size_3 %>% 
  group_by(SITE, YEAR) %>%
  summarize('mean' = round(mean(`SIZE`), digits=2),
            'median' = round(median(`SIZE`), digits = 2),
            'max' = max(`SIZE`),
            'SD' = round(sd(`SIZE`),digits=2), 
            'n' = sum(`COUNT`),
            'se' = round(sd(`SIZE`)/sqrt(length(`SIZE`)), digits = 2))

size_sum_3
```

##Dataframe: All 5 sites expanded from Frequency to Case Format (n=1,899)
```{r expanded for frequency}
sz_expand_3 <- lb_size_3[rep(1:nrow(lb_size_3), lb_size_3[["COUNT"]]), ]
sz_expand_3$SITE<-as.factor(sz_expand_3$SITE)
sz_expand_3
```

```{r}
limits <- aes(ymax = size_sum_3$mean + size_sum_3$se,
              ymin = size_sum_3$mean - size_sum_3$se)

p <- ggplot(data = size_sum_3, aes(x = factor(SITE), y = mean,
               fill = YEAR)) +
  geom_bar(stat = "identity", position = dodge, width=0.8) +
  theme_minimal()+
  geom_errorbar(limits, position = position_dodge(0.95), width = 0.25) +
  scale_color_brewer(palette="Pastel2")+
  scale_fill_discrete(name = "Year")+
  labs(x = "Site", y = "Mean Lobster Size") +
  ggtitle("Mean Lobster Size by Site and Year\n2012, 2017" )
  
  
p

```

```{r}
ggbarplot(size_sum_3, x = "SITE", y = "mean", color = "YEAR", fill="YEAR",
          palette = c("#00AFBB", "#E7B800"), position = position_dodge(0.8), add = c("mean_se", "jitter"))

```


```{r}
sz_expand_3$YEAR <- factor(sz_expand_3$YEAR, 
                  levels = c(2012, 2017))

b<-ggboxplot(sz_expand_3, x = "SITE", y = "SIZE", color = "YEAR",
          palette = c("#00AFBB", "#E7B800"))
b
```

##SITE: MPA sites 
##YEAR: 2012 and 2017
##SIZE: EXPANDED 
```{r }
mpa_sz_3 <- sz_expand_3 %>% 
  filter(MPA == "Yes") %>% 
  select(YEAR, SITE, SIZE)
mpa_sz_3 
```

```{r}
mpa_sz_bplot<-ggboxplot(mpa_sz_3, x = "YEAR", y = "SIZE", 
          color = "YEAR", palette = c("#00AFBB", "#E7B800"),
        ylab = "SIZE", xlab = "YEAR")+
  labs(title = "Lobster SIZE")
mpa_sz_bplot
```

##NAPL Size Comparison 
```{r napl comparison}
npl_sz <- sz_expand_3 %>% 
  filter(SITE == "NAPL") %>% 
  select(YEAR, SITE, SIZE)
npl_sz 

npl_sz_bplot<-ggboxplot(npl_sz, x = "YEAR", y = "SIZE", 
          color = "YEAR", palette = c("#00AFBB", "#E7B800"),
        ylab = "SIZE", xlab = "YEAR")+
  labs(title = "NAPL Lobster SIZE")
npl_sz_bplot

```

*gghistogram(npl_sz, x = "SIZE",
   add = "mean", rug = TRUE,
   color = "YEAR", fill = "YEAR",
   palette = c("#00AFBB", "#E7B800"),
   xlab = Lobster Size)*

##t-test for change in mean lobster size at each site 
###f-test: Do the two populations have the same variances?

```{r}
napl_ftest <- var.test(weight ~ group, data = npl_sz)
napl_ftest
```


```{r ivee comparison}
lb_sz_mpa_ivee <- lb_sz_expand_12_17 %>% 
  filter(SITE == "IVEE") %>% 
  select(YEAR, SITE, SIZE)
lb_sz_mpa_ivee 

lb_sz_mpa_ivee_plot<-ggboxplot(lb_sz_mpa_ivee, x = "YEAR", y = "SIZE", 
          color = "YEAR", palette = c("#00AFBB", "#E7B800"),
        ylab = "SIZE", xlab = "YEAR")+
  labs(title = "IVEE Lobster SIZE")
lb_sz_mpa_ivee_plot
```




